Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-05-30 paper.tex
Update on Overleaf.

  \textit{Context:} The integration of Rust into kernel development is a transformative endeavor aimed
  at enhancing system security and reliability by leveraging Rust's strong memory safety
  guarantees. 
  %This systematic literature review examines the current state of research and practice regarding the use of Rust in the kernel development.
  \textit{Objective:} We aim to find the current advances in using Rust in Kernel
  development to reduce the number of memory safety
  vulnerabilities in one of the most critical pieces of software that underpins all modern
  applications.
  \textit{Method:} By analyzing a broad spectrum of studies, we identify the advantages Rust offers,
  %such as reducing vulnerabilities like buffer overflows and use-after-free errors, which are
  %prevalent in C-based kernel development. The review also 
  highlight the challenges faced,
  %including integration hurdles with existing C codebases, performance considerations, 
  and emphasise the need for community consensus on Rust's adoption.
  \textit{Results:} Our findings suggest that while the initial implementations of Rust in the kernel
  show promising results in terms of safety and stability, significant challenges remain. These challenges
  include achieving seamless interoperability with existing kernel components, maintaining
  performance, and ensuring adequate support and tooling for developers.
  \textit{Conclusions:} This study 
  %provides a comprehensive overview of the
  %potential and challenges of incorporating Rust into kernel development. It 
  underscores the need for
  continued research and practical implementation efforts to fully realize the benefits of Rust. By
  addressing these challenges, the integration of Rust could mark a significant step forward in the
  evolution of operating system development towards safer and more reliable systems.

@@

In the ever-evolving landscape of software development, the reliability and security of computer
systems stand as a paramount concern for all parties involved. Modern software is constructed by
building ever more complex abstractions, one on top of the other. Thus, if we aim to have a secure
system, we must start to peel back all the layers and tackle one of the fundamental abstractions in
computer science: the programming language. Programming languages that provide and enforce memory
safety eliminate whole classes of bugs such as buffer overflows, dangling pointers, and memory leaks
which have been implicated in a myriad of security vulnerabilities and system crashes.

>>>>

  \textit{\textbf{Context:}} The integration of Rust into kernel development is a transformative endeavor aimed
  at enhancing system security and reliability by leveraging Rust's strong memory safety
  guarantees. 
  %This systematic literature review examines the current state of research and practice regarding the use of Rust in the kernel development.
  \textit{\textbf{Objective:}} We aim to find the current advances in using Rust in Kernel
  development to reduce the number of memory safety
  vulnerabilities in one of the most critical pieces of software that underpins all modern
  applications.
  \textit{\textbf{Method:}} By analyzing a broad spectrum of studies, we identify the advantages Rust offers,
  %such as reducing vulnerabilities like buffer overflows and use-after-free errors, which are
  %prevalent in C-based kernel development. The review also 
  highlight the challenges faced,
  %including integration hurdles with existing C codebases, performance considerations, 
  and emphasise the need for community consensus on Rust's adoption.
  \textit{\textbf{Results:}} Our findings suggest that while the initial implementations of Rust in the kernel
  show promising results in terms of safety and stability, significant challenges remain. These challenges
  include achieving seamless interoperability with existing kernel components, maintaining
  performance, and ensuring adequate support and tooling for developers.
  \textit{\textbf{Conclusions:}} This study 
  %provides a comprehensive overview of the
  %potential and challenges of incorporating Rust into kernel development. It 
  underscores the need for
  continued research and practical implementation efforts to fully realize the benefits of Rust. By
  addressing these challenges, the integration of Rust could mark a significant step forward in the
  evolution of operating system development towards safer and more reliable systems.

@@

In the ever-evolving landscape of software development, the reliability and security of computer
systems stand as a paramount concern for all parties involved. Modern software is constructed by
building ever more complex abstractions, one on top of the other. Thus, if we aim to have a secure
system, we must start to peel back all the layers and tackle one of the fundamental abstractions in
computer science: the programming language. Programming languages that provide and enforce memory
safety eliminate whole classes of bugs, such as buffer overflows, dangling pointers, and memory leaks
which have been implicated in a myriad of security vulnerabilities and system crashes.
